### 2020-03-03 doc/icfp20/conclusion.tex
the most promising way -> a promising way

We believe that functional programming, and in particular functional
programming with dependent types, is the most promising way to do software
engineering going forward. The languages and tools are perhaps not yet
as finely polished and rich as those typically used in production
software, but they are fundamentally far more powerful, and thus once
the infrastructure (and training of programmers) catches up should
become the languages of choice.

>>>>

We believe that functional programming, and in particular functional
programming with dependent types, is a promising way to do software
engineering going forward. The languages and tools are perhaps not yet
as finely polished and rich as those typically used in production
software, but they are fundamentally far more powerful, and thus once
the infrastructure (and training of programmers) catches up should
become the languages of choice.
